Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-10-18 Ch1_movement_rates/Ch1_Figures.Rmd
updating figures

knitr::kable(table1)
write.csv(table1, file = "Ch1_movement_rates/Figures/table1.csv")

@@

@@

```{r}
# Visualize distribution and data points
vlines <- summary(indiv_moverate$movrate)[c(1,3,6)]

indiv_moverate %>%
  ggplot(., aes(x = movrate, y = 0.002)) +
  geom_point(size = 3, alpha = 0.8) +
  geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
                color = "black", alpha = 0.8, size = 1) +
  labs(x = "Movement Rate (meters/minute)", y = "Density",
       title = "Lognormal fit to movement rates",
       subtitle = "Each dot is an individual") +
  geom_vline(xintercept = vlines, color = my.cols1[4], size = 1, lty = 2) +
  scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60),
                     labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) +
  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
  theme_bw()

# ggsave2(filename = "Ch1_movement_rates/Figures/logfit_cp.png")
```

```{r include=FALSE}
# The average movement rate for this sample of the population (the 12 individuals) is the average of the movement rate for each individual:

# mean(indiv_moverate$movrate)
# 27.94211 meters/minute

# In a complete pooling approach, we take this average movement rate and use it as the parameter for our exponential distribution, from which we draw the movement distance at each time step.

## Compare exponential movement distances to full dataset ----------------------------------

movrate_cp <- mean(indiv_moverate$movrate)
movrate_cp_ln <- as.numeric(exp(logfit$estimate[1]))

# test <- data.frame(mpm = rexp(500, rate = 1/movrate_cp))
#
# test %>%
#   ggplot(., aes(x = mpm)) +
#   geom_histogram(aes(y = ..density..)) +
#   stat_function(fun = dexp, args = list(rate = 1/movrate_cp), color = "red")

ptpl %>%
  ggplot(., aes(x = mpm)) +
  geom_histogram(aes(y = ..density..)) +
  stat_function(fun = dexp, args = list(rate = 1/movrate_cp), color = my.cols1[4], size = 1) +
  stat_function(fun = dexp, args = list(rate = 1/movrate_cp_ln), color = my.cols1[3], size = 1, alpha = 0.8) +
  labs(title = "Histogram of movement distances per minute from data set",
       x = "Movement distance per minute",
       y = "Density",
       caption = "Orange line is exponential density using average movement rate for population \n
       Yellow line shows exponential density using mean estimate from lognormal fit to movement rates") +
  theme_bw()

```{r include=FALSE}
## Visualize mov rates ---------------
pp_1 <- sort(round(fam_moverate$movrate,3))

### Compare lognorm fits CP and PP -----------

logfit_fam <- fitdist(pp_1, distr = 'lnorm')
# normfit <- fitdist(indiv_moverate$movrate, distr = "norm")

# Mean using the fit
# exp(logfit_fam$estimate[1])

```{r}
# Visualize distribution and data points
vlines_fam <- summary(fam_moverate$movrate)[c(1,3,6)]

indiv_moverate %>%
  ggplot(., aes(x = movrate, y = 0.002)) +
  # stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
  #               color = "black", alpha = 0.8, size = 1) +
  # geom_point(size = 3, alpha = 0.8) +
  # geom_vline(xintercept = vlines, color = "black", size = 1, lty = 2) +
  # scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60),
  #                    labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
                color = my.cols1[4], alpha = 0.8, size = 1) +
  geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
  geom_vline(xintercept = vlines_fam, color = my.cols1[4], size = 1, lty = 2) +
  scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines_fam[1], 20, vlines_fam[2], vlines_fam[3], 60),
                     labels = c(0, "Min.", 20, "Median.", "Max.", 60)) +
  labs(x = "Movement Rate (meters/minute)", y = "Density",
       title = "Lognormal fit to family group movement rates") +
  theme_bw()

# ggsave2(filename = "Ch1_movement_rates/Figures/logfit_pp.png")

```{r include=FALSE}
## Visualize mov rates ---------------
pp_1 <- sort(round(fam_moverate$movrate,3))

### Compare lognorm fits CP and PP -----------

logfit_fam <- fitdist(fam_moverate$movrate, distr = 'lnorm')
# normfit <- fitdist(indiv_moverate$movrate, distr = "norm")

# Mean using the fit
exp(logfit_fam$estimate[1])

```{r}
# Visualize distribution and data points
vlines_fam <- summary(fam_moverate$movrate)[c(1,3,6)]

indiv_moverate %>%
  ggplot(., aes(x = movrate, y = 0.002)) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
                color = "black", alpha = 0.8, size = 1) +
  geom_point(size = 3, alpha = 0.8) +
  geom_vline(xintercept = vlines, color = "black", size = 1, lty = 2) +
  scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60),
                     labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) +
  # stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
  #               color = my.cols1[4], alpha = 0.8, size = 1) +
  geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
  # geom_vline(xintercept = vlines_fam, color = my.cols1[4], size = 1, lty = 2) +
  labs(x = "Movement Rate (meters/minute)",
       # title = "Average movement rates lognormal fits",
       y = "Density") +
  theme_bw()
```

```{r}
## PP w/fam moverates ---------------------------------------
# Meaning, we use the average movement rate for each family group as the parameter for an exponential from which we draw movement distances for the simulation.

fam_moverate %>%
  arrange(., movrate) -> fam_moverate

fam_moverate %>%
  ggplot(., aes(x = movrate, y = 0, color = movrate)) +
  geom_point(size = 3) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]),
                color = my.cols1[4], alpha = 0.8, size = 1) +
  xlim(0, 60) +
  labs(title = "Lognormal fitted to family group",
       x = "Movement rate",
       y = "Density") +
  scale_color_viridis_c() +
  theme_bw() +
  theme(legend.position = "none") -> pp_logfit

mycols2 <- viridisLite::viridis(7)
expcurves_pp1 <- purrr::map(seq(1:7), function(y)
  stat_function(fun = dexp, args = list(rate = 1/fam_moverate$movrate[y]), color = mycols2[y], alpha = 0.8))

ggplot() +
  expcurves_pp1 +
  xlim(-1, 125) +
  labs(title = "Movement distance exponential draws", x = 'Movement Distance', y = "Density") +
  theme_bw() -> pp_expdraws

cowplot::plot_grid(pp_logfit, pp_expdraws)
# ggsave2(filename = "Ch1_movement_rates/Figures/pp_logfit_plus_exp.png")
```

```{r include=FALSE}
# This one looks at individual variation.
# We will sample 20 individuals, 3 times from the lognormal distribution that describes movement rates for the population
logfit <- fitdist(indiv_moverate$movrate, distr = 'lnorm')

n.individuals <- 20
m_1 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3))
m_2 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3))
m_3 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3))

logfitdraw <- data.frame(indv = 1:20, m_1 = m_1, m_2 = m_2, m_3 = m_3)

indiv_moverate %>%
  ggplot(., aes(x = movrate, y = 0)) +
  geom_point(size = 5) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]), color = "black", alpha = 0.8) +
  geom_point(data = logfitdraw, aes(x = m_1, color = factor(indv), y = 0.005), size = 3) +
  geom_point(data = logfitdraw, aes(x = m_2, color = factor(indv), y = 0.006), size = 3) +
  geom_point(data = logfitdraw, aes(x = m_3, color = factor(indv), y = 0.007), size = 3) +
  # scale_color_viridis_d(option="magma") +
  scale_color_viridis_d() +
  xlim(0, 60) +
  labs(title = "Sampling individuals from lognormal",
       x = "Movement rate",
       y = "Density") +
  theme_bw() +
  theme(legend.position = "none") -> plot.logfitdraw

plot.logfitdraw

mycols <- viridisLite::viridis(20)

expcurves_m1 <- purrr::map(seq(1:n.individuals), function(y)
  stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_1[y]), color = mycols[y], alpha = 0.8))

expcurves_m2 <- purrr::map(seq(1:n.individuals), function(y)
  stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_2[y]), color = mycols[y], alpha = 0.8))

expcurves_m3 <- purrr::map(seq(1:n.individuals), function(y)
  stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_3[y]), color = mycols[y], alpha = 0.8))

logfitdraw %>%
  ggplot() +
  expcurves_m1 +
  expcurves_m2 +
  expcurves_m3 +
  xlim(-1, 125) +
  labs(title = "Movement distance Exponential Draws", x = 'Movement Distance', y = "Density") +
  theme_bw() -> expdraws
expdraws

cowplot::plot_grid(plot.logfitdraw, expdraws)

# ggsave2(filename = "Ch1_movement_rates/Figures/Sampling_indivs_lnorm.png")
```

```{r}
# Bring data --------------------------------------------
load("Ch1_movement_rates/sims_backup/datagen_cp.RData")
load("Ch1_movement_rates/sims_backup/datagen_pp.RData")
load("Ch1_movement_rates/sims_backup/datagen_np.RData")
load("Ch1_movement_rates/sims_backup/datagen_ppi.RData")

load("Ch1_movement_rates/sims_backup/weib_cp.RData")
load("Ch1_movement_rates/sims_backup/weib_pp.RData")
load("Ch1_movement_rates/sims_backup/weib_np.RData")
load("Ch1_movement_rates/sims_backup/weib_ppi.RData")

@@

cp.summ.df %>%
  dplyr::select(av.disp, dsprsn, popu) %>%
  mutate(model = "cp") %>%
  bind_rows(., pp.summ.df %>%
              dplyr::select(av.disp, dsprsn, model) %>% 
              mutate(model = "pp")) %>%
  bind_rows(., np.summ.df %>%
              dplyr::select(av.disp, dsprsn, popu) %>%
              mutate(model = paste0("np_", popu))) %>% 
  bind_rows(., ppi.summ.df %>% 
              dplyr::select(av.disp, dsprsn, model) %>% 
              mutate(model = "ppi")) %>% 
  mutate(model = factor(model, levels = c("cp", "pp", "ppi","np_1", "np_2", "np_3"))) -> disp_df

disp_df %>%
  group_by(., model) %>%
  sample_n(., 100) %>%
  ggplot(., aes(y = dsprsn, x = model)) +
  geom_boxplot() +
  geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Dispersion", y = "Dispersion in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> p_dispersion

@@

weib.boot.cp %>%
  mutate(model = "cp") %>%
  dplyr::select(., est.shape, est.scale, boot, model) %>%
  bind_rows(., weib.boot.pp %>%
              dplyr::select(., est.shape, est.scale, boot, model)) %>%
  bind_rows(., weib.boot.ppi %>%
              # mutate(model = paste0(model, "_", popu)) %>% 
              dplyr::select(., est.shape, est.scale, boot, model)) %>%
  bind_rows(., weib.boot.np %>%
              mutate(model = paste0("np_", popu)) %>%
              dplyr::select(., est.shape, est.scale, boot, model)) -> joint_weib

joint_weib %>% 
  mutate(model = factor(model, levels = c("cp", "pp", "ppi", "np_1", "np_2", "np_3"))) -> joint_weib
```

```{r}
joint_weib %>%
  group_by(model) %>%
  sample_n(., 200) %>%
  ggplot(., aes(x = model, y = est.shape)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(position = position_jitter(0.1)) +
  labs(title = "Shape") +
  theme_bw() -> weib_shape

joint_weib %>%
  group_by(model) %>%
  sample_n(., 200) %>%
  ggplot(., aes(x = model, y = est.scale)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(position = position_jitter(0.1)) +
  labs(title = "Scale") +
  theme_bw() -> weib_scale

@@

>>>>

knitr::kable(table1)
# write.csv(table1, file = "Ch1_movement_rates/Figures/table1.csv")

@@

In process

@@

<!-- ```{r} -->
<!-- # Visualize distribution and data points -->
<!-- vlines <- summary(indiv_moverate$movrate)[c(1,3,6)] -->

<!-- indiv_moverate %>% -->
<!--   ggplot(., aes(x = movrate, y = 0.002)) + -->
<!--   geom_point(size = 3, alpha = 0.8) + -->
<!--   geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) + -->
<!--   stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]), -->
<!--                 color = "black", alpha = 0.8, size = 1) + -->
<!--   labs(x = "Movement Rate (meters/minute)", y = "Density", -->
<!--        title = "Lognormal fit to movement rates", -->
<!--        subtitle = "Each dot is an individual") + -->
<!--   geom_vline(xintercept = vlines, color = my.cols1[4], size = 1, lty = 2) + -->
<!--   scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60), -->
<!--                      labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) + -->
<!--   #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) + -->
<!--   theme_bw() -->

<!-- # ggsave2(filename = "Ch1_movement_rates/Figures/logfit_cp.png") -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- # The average movement rate for this sample of the population (the 12 individuals) is the average of the movement rate for each individual: -->

<!-- # mean(indiv_moverate$movrate) -->
<!-- # 27.94211 meters/minute -->

<!-- # In a complete pooling approach, we take this average movement rate and use it as the parameter for our exponential distribution, from which we draw the movement distance at each time step. -->

<!-- ## Compare exponential movement distances to full dataset ---------------------------------- -->

<!-- movrate_cp <- mean(indiv_moverate$movrate) -->
<!-- movrate_cp_ln <- as.numeric(exp(logfit$estimate[1])) -->

<!-- # test <- data.frame(mpm = rexp(500, rate = 1/movrate_cp)) -->
<!-- # -->
<!-- # test %>% -->
<!-- #   ggplot(., aes(x = mpm)) + -->
<!-- #   geom_histogram(aes(y = ..density..)) + -->
<!-- #   stat_function(fun = dexp, args = list(rate = 1/movrate_cp), color = "red") -->

<!-- ptpl %>% -->
<!--   ggplot(., aes(x = mpm)) + -->
<!--   geom_histogram(aes(y = ..density..)) + -->
<!--   stat_function(fun = dexp, args = list(rate = 1/movrate_cp), color = my.cols1[4], size = 1) + -->
<!--   stat_function(fun = dexp, args = list(rate = 1/movrate_cp_ln), color = my.cols1[3], size = 1, alpha = 0.8) + -->
<!--   labs(title = "Histogram of movement distances per minute from data set", -->
<!--        x = "Movement distance per minute", -->
<!--        y = "Density", -->
<!--        caption = "Orange line is exponential density using average movement rate for population \n -->
<!--        Yellow line shows exponential density using mean estimate from lognormal fit to movement rates") + -->
<!--   theme_bw() -->

<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- ## Visualize mov rates --------------- -->
<!-- pp_1 <- sort(round(fam_moverate$movrate,3)) -->

<!-- ### Compare lognorm fits CP and PP ----------- -->

<!-- logfit_fam <- fitdist(pp_1, distr = 'lnorm') -->
<!-- # normfit <- fitdist(indiv_moverate$movrate, distr = "norm") -->

<!-- # Mean using the fit -->
<!-- # exp(logfit_fam$estimate[1]) -->

<!-- ``` -->

<!-- ```{r} -->
<!-- # Visualize distribution and data points -->
<!-- vlines_fam <- summary(fam_moverate$movrate)[c(1,3,6)] -->

<!-- indiv_moverate %>% -->
<!--   ggplot(., aes(x = movrate, y = 0.002)) + -->
<!--   # stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]), -->
<!--   #               color = "black", alpha = 0.8, size = 1) + -->
<!--   # geom_point(size = 3, alpha = 0.8) + -->
<!--   # geom_vline(xintercept = vlines, color = "black", size = 1, lty = 2) + -->
<!--   # scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60), -->
<!--   #                    labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) + -->
<!--   stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]), -->
<!--                 color = my.cols1[4], alpha = 0.8, size = 1) + -->
<!--   geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) + -->
<!--   geom_vline(xintercept = vlines_fam, color = my.cols1[4], size = 1, lty = 2) + -->
<!--   scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines_fam[1], 20, vlines_fam[2], vlines_fam[3], 60), -->
<!--                      labels = c(0, "Min.", 20, "Median.", "Max.", 60)) + -->
<!--   labs(x = "Movement Rate (meters/minute)", y = "Density", -->
<!--        title = "Lognormal fit to family group movement rates") + -->
<!--   theme_bw() -->

<!-- # ggsave2(filename = "Ch1_movement_rates/Figures/logfit_pp.png") -->

<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- ## Visualize mov rates --------------- -->
<!-- pp_1 <- sort(round(fam_moverate$movrate,3)) -->

<!-- ### Compare lognorm fits CP and PP ----------- -->

<!-- logfit_fam <- fitdist(fam_moverate$movrate, distr = 'lnorm') -->
<!-- # normfit <- fitdist(indiv_moverate$movrate, distr = "norm") -->

<!-- # Mean using the fit -->
<!-- exp(logfit_fam$estimate[1]) -->

<!-- ``` -->

<!-- ```{r} -->
<!-- # Visualize distribution and data points -->
<!-- vlines_fam <- summary(fam_moverate$movrate)[c(1,3,6)] -->

<!-- indiv_moverate %>% -->
<!--   ggplot(., aes(x = movrate, y = 0.002)) + -->
<!--   stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]), -->
<!--                 color = "black", alpha = 0.8, size = 1) + -->
<!--   geom_point(size = 3, alpha = 0.8) + -->
<!--   geom_vline(xintercept = vlines, color = "black", size = 1, lty = 2) + -->
<!--   scale_x_continuous(limits = c(0, 70), breaks = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60), -->
<!--                      labels = c(0, "Min.", 20, "Median.", 40, "Max.", 60)) + -->
<!--   # stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]), -->
<!--   #               color = my.cols1[4], alpha = 0.8, size = 1) + -->
<!--   geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) + -->
<!--   # geom_vline(xintercept = vlines_fam, color = my.cols1[4], size = 1, lty = 2) + -->
<!--   labs(x = "Movement Rate (meters/minute)", -->
<!--        # title = "Average movement rates lognormal fits", -->
<!--        y = "Density") + -->
<!--   theme_bw() -->
<!-- ``` -->

<!-- ```{r} -->
<!-- ## PP w/fam moverates --------------------------------------- -->
<!-- # Meaning, we use the average movement rate for each family group as the parameter for an exponential from which we draw movement distances for the simulation. -->

<!-- fam_moverate %>% -->
<!--   arrange(., movrate) -> fam_moverate -->

<!-- fam_moverate %>% -->
<!--   ggplot(., aes(x = movrate, y = 0, color = movrate)) + -->
<!--   geom_point(size = 3) + -->
<!--   stat_function(fun = dlnorm, args = list(meanlog = logfit_fam$estimate[1], sdlog = logfit_fam$estimate[2]), -->
<!--                 color = my.cols1[4], alpha = 0.8, size = 1) + -->
<!--   xlim(0, 60) + -->
<!--   labs(title = "Lognormal fitted to family group", -->
<!--        x = "Movement rate", -->
<!--        y = "Density") + -->
<!--   scale_color_viridis_c() + -->
<!--   theme_bw() + -->
<!--   theme(legend.position = "none") -> pp_logfit -->

<!-- mycols2 <- viridisLite::viridis(7) -->
<!-- expcurves_pp1 <- purrr::map(seq(1:7), function(y) -->
<!--   stat_function(fun = dexp, args = list(rate = 1/fam_moverate$movrate[y]), color = mycols2[y], alpha = 0.8)) -->

<!-- ggplot() + -->
<!--   expcurves_pp1 + -->
<!--   xlim(-1, 125) + -->
<!--   labs(title = "Movement distance exponential draws", x = 'Movement Distance', y = "Density") + -->
<!--   theme_bw() -> pp_expdraws -->

<!-- cowplot::plot_grid(pp_logfit, pp_expdraws) -->
<!-- # ggsave2(filename = "Ch1_movement_rates/Figures/pp_logfit_plus_exp.png") -->
<!-- ``` -->

<!-- ```{r include=FALSE} -->
<!-- # This one looks at individual variation. -->
<!-- # We will sample 20 individuals, 3 times from the lognormal distribution that describes movement rates for the population -->
<!-- logfit <- fitdist(indiv_moverate$movrate, distr = 'lnorm') -->

<!-- n.individuals <- 20 -->
<!-- m_1 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3)) -->
<!-- m_2 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3)) -->
<!-- m_3 <- sort(round(rlnorm(n.individuals, meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),3)) -->

<!-- logfitdraw <- data.frame(indv = 1:20, m_1 = m_1, m_2 = m_2, m_3 = m_3) -->

<!-- indiv_moverate %>% -->
<!--   ggplot(., aes(x = movrate, y = 0)) + -->
<!--   geom_point(size = 5) + -->
<!--   stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]), color = "black", alpha = 0.8) + -->
<!--   geom_point(data = logfitdraw, aes(x = m_1, color = factor(indv), y = 0.005), size = 3) + -->
<!--   geom_point(data = logfitdraw, aes(x = m_2, color = factor(indv), y = 0.006), size = 3) + -->
<!--   geom_point(data = logfitdraw, aes(x = m_3, color = factor(indv), y = 0.007), size = 3) + -->
<!--   # scale_color_viridis_d(option="magma") + -->
<!--   scale_color_viridis_d() + -->
<!--   xlim(0, 60) + -->
<!--   labs(title = "Sampling individuals from lognormal", -->
<!--        x = "Movement rate", -->
<!--        y = "Density") + -->
<!--   theme_bw() + -->
<!--   theme(legend.position = "none") -> plot.logfitdraw -->

<!-- plot.logfitdraw -->

<!-- mycols <- viridisLite::viridis(20) -->

<!-- expcurves_m1 <- purrr::map(seq(1:n.individuals), function(y) -->
<!--   stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_1[y]), color = mycols[y], alpha = 0.8)) -->

<!-- expcurves_m2 <- purrr::map(seq(1:n.individuals), function(y) -->
<!--   stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_2[y]), color = mycols[y], alpha = 0.8)) -->

<!-- expcurves_m3 <- purrr::map(seq(1:n.individuals), function(y) -->
<!--   stat_function(fun = dexp, args = list(rate = 1/logfitdraw$m_3[y]), color = mycols[y], alpha = 0.8)) -->

<!-- logfitdraw %>% -->
<!--   ggplot() + -->
<!--   expcurves_m1 + -->
<!--   expcurves_m2 + -->
<!--   expcurves_m3 + -->
<!--   xlim(-1, 125) + -->
<!--   labs(title = "Movement distance Exponential Draws", x = 'Movement Distance', y = "Density") + -->
<!--   theme_bw() -> expdraws -->
<!-- expdraws -->

<!-- ``` -->

<!-- ```{r} -->

<!-- cowplot::plot_grid(plot.logfitdraw, expdraws) -->

<!-- # ggsave2(filename = "Ch1_movement_rates/Figures/Sampling_indivs_lnorm.png") -->
<!-- ``` -->

```{r}
# Bring data --------------------------------------------
load("Ch1_movement_rates/sims_backup/datagen_cp.RData")
load("Ch1_movement_rates/sims_backup/datagen_pp.RData")
load("Ch1_movement_rates/sims_backup/datagen_np.RData")
#load("Ch1_movement_rates/sims_backup/datagen_ppi.RData")

load("Ch1_movement_rates/sims_backup/weib_cp.RData")
load("Ch1_movement_rates/sims_backup/weib_pp.RData")
load("Ch1_movement_rates/sims_backup/weib_np.RData")
#load("Ch1_movement_rates/sims_backup/weib_ppi.RData")

@@

cp.summ.df %>%
  dplyr::select(av.disp, dsprsn, model) %>% 
  bind_rows(., pp.summ.df %>%
              dplyr::select(av.disp, dsprsn, model)) %>%
  bind_rows(., np.summ.df %>%
              dplyr::select(av.disp, dsprsn,  model) %>%
              mutate(model = "np")) %>% 
  # bind_rows(., ppi.summ.df %>% 
  #             dplyr::select(av.disp, dsprsn, model) %>% 
  #             mutate(model = "ppi")) %>% 
  mutate(model = factor(model, levels = c("cp", "pp",
                                          #"ppi",
                                          #"np_1", "np_2", "np_3",
                                          "np"))) -> disp_df
```

```{r}
disp_df %>%
  group_by(., model) %>%
  sample_n(., 100) %>%
  ggplot(., aes(y = dsprsn, x = model)) +
  geom_boxplot() +
  geom_point(color = "grey", alpha = 0.5) +
  labs(title = "Dispersion", y = "Dispersion in meters", x = "Model") +
  theme_bw() +
  theme(legend.position = "none") -> p_dispersion

@@

weib.boot.cp %>%
  dplyr::select(., est.shape, est.scale, boot, model) %>%
  bind_rows(., weib.boot.pp %>%
              dplyr::select(., est.shape, est.scale, boot, model)) %>%
  # bind_rows(., weib.boot.ppi %>%
  #             # mutate(model = paste0(model, "_", popu)) %>% 
  #             dplyr::select(., est.shape, est.scale, boot, model)) %>%
  bind_rows(., weib.boot.np %>%
              mutate(model = "np") %>%
              dplyr::select(., est.shape, est.scale, boot, model)) -> joint_weib

joint_weib %>% 
  mutate(model = factor(model, levels = c("cp", "pp",
                                          # "ppi", "np_1", "np_2", "np_3"
                                          "np"))) -> joint_weib
```

```{r}
joint_weib %>%
  group_by(model) %>%
  sample_n(., 100) %>%
  ggplot(., aes(x = model, y = est.shape)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(position = position_jitter(0.1)) +
  labs(title = "Shape") +
  theme_bw() -> weib_shape

joint_weib %>%
  group_by(model) %>%
  sample_n(., 100) %>%
  ggplot(., aes(x = model, y = est.scale)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(position = position_jitter(0.1)) +
  labs(title = "Scale") +
  theme_bw() -> weib_scale

@@

```
# Table 2 - results
